---
title: "Tomato 3rd Test Run"
output: html_notebook
---

96 ddRAD samples\
i2 > restriction enzymes: PstI (1st) and MseI (2nd)\
i6 > restriction enzymes: NsiI (1st) and MseI (2nd)\
i3 > restriction enzymes: PstI (1st)\
i7 > restriction enzymes: NsiI (1st)\
Read length: 75\
  
Pre-process:\
process_rapture.py to demutiplex and remove reads with double barcodes or barcodes not found.\
process_radtags to eliminate reads with low quality score (<20) or ambiguous RAD-tags.\

---

### Input reads summary table
```{r}
reads_table <- read.table('/home/dang/tomato/test3/cleaned/i7/process_radtags_summary.txt', header = TRUE)
head(reads_table)
tail(reads_table)
```

### Calculate median here
```{r}
median_retained <- median(reads_table$Retained_Reads)
median_retained
median_lowQ <- median(reads_table$Low_Quality)
median_lowQ
median_AmbRAD <- median(reads_table$Ambiguous_RAD.Tag)
median_AmbRAD
median_total <- median(reads_table$Total)
median_total
```

### Use geom_point from ggplot2 to plot
```{r}
library(ggplot2)
```

### Reads count point plot distribution along samples
  
#### After process_rapture.py
```{r}
p <- ggplot(data=reads_table, aes(x=Total/1000, y=ID))
p <- p + geom_point() 
p <- p + theme(axis.line = element_line(colour = "black")) + labs(x="Count (10^3)")
p <- p + geom_vline(xintercept = median_total/1000, color='red')
p
```
  
#### After process_radtags
```{r}
p <- ggplot(data=reads_table, aes(x=Retained_Reads/1000, y=ID))
p <- p + geom_point() 
p <- p + geom_point(data=reads_table, aes(x=Total/1000, y=ID), alpha=0.25)
p <- p + theme(axis.line = element_line(colour = "black")) + labs(x="Count (10^3)")
p <- p + geom_vline(xintercept = median_retained/1000, color='red')
p <- p + geom_vline(xintercept = median_total/1000, color='red', alpha=0.25)
p
```
  
#### Explore on low quality reads
```{r}
p <- ggplot(data=reads_table, aes(x=log10(Retained_Reads), y=ID))
p <- p + geom_point(color="black") 
p <- p + geom_point(data=reads_table, aes(x=log10(Low_Quality), y=ID), color="red")
p <- p + theme(axis.line = element_line(colour = "black")) + labs(x="Count (log10)")
p <- p + geom_vline(xintercept = log10(median_retained), color='black')
p <- p + geom_vline(xintercept = log10(median_lowQ), color="red")
p
```
  
#### Explore on ambiguous RAD-tags
```{r}
p <- ggplot(data=reads_table, aes(x=log10(Retained_Reads), y=ID))
p <- p + geom_point(color="black") 
p <- p + geom_point(data=reads_table, aes(x=log10(Ambiguous_RAD.Tag
), y=ID), color="darkgreen")
p <- p + theme(axis.line = element_line(colour = "black")) + labs(x="Count (log10)")
p <- p + geom_vline(xintercept = log10(median_retained), color='black')
p <- p + geom_vline(xintercept = log10(median_AmbRAD), color="darkgreen")
p
```


